\newcommand*{\req}[5]{{\noindent{IDENTIFIER: \textbf{#1}}}\\{DESCRIPTION: #2\\}{PURPOSE: #3\\}{I/O: #4\\}{ACTORS/TRIGGERS: #5\\}}

\section*{Functional Requirements}
\singlespacing
\noindent{\textbf{Functional Req 1.}

\req{Landing/Home Page}
{User is greeted with GUS' homepage when they go the website }
{To have a landing page}
{I/O}
{User enters "www.url of GUS.ext" in a browser}

\noindent{\textbf{Functional Req 2.}

\req{Search Bar present}
{On the homepage, a search box for querying music is present.}
{Easy and straightforward way to query music}
{I/O}
{User is on homepage}

\noindent{\textbf{Functional Req 3.}

\req{Live Query results}
{As a user is typing a query in the search bar, a certain number of results are displayed in a list view below the bar in a live updating fashion. }
{So user can potentially access a result without having to query in its entirety}
{I/O}
{User types the name of existent music}

\noindent{\textbf{Functional Req 4.}

\req{Select Song/Artist/Album}
{Near the search bar is a selection for querying a song, artist, or album.}
{To further refine the search to match the users wants.}
{I/O}
{User is on homepage.}

\noindent{\textbf{Functional Req 5.}

\req{Valid Song Search Results}
{When a user chooses to query a song, and results for that song indeed exist, then they will be taken to a new page and presented with a list of songs of that name.}
{To give the user a list of common songs matching the desired name.}
{I/O}
{User queries a song that is present on streaming services}

\noindent{\textbf{Functional Req 6.}

\req{Invalid Song Search Results}
{When a user chooses to query a song, and no results for that name are found, then they will be taken to a new page and presented with "no songs found".}
{To inform the user that their query did not return any results}
{I/O}
{User queries a string that doesn't match songs on any streaming services}

\noindent{\textbf{Functional Req 7.}

\req{Valid Artist Search Results}
{When a user chooses to query an artist, and results for that artist indeed exist, then they will be taken to a new page and presented with a list of artists of that name.}
{To give the user a list of common artists matching the desired name.}
{I/O}
{User queries an artist that is present on streaming services}

\noindent{\textbf{Functional Req 8.}

\req{Invalid Artist Search Results}
{When a user chooses to query an artist, and no results for that name are found, then they will be taken to a new page and presented with "no artists found".}
{To inform the user that their query did not return any results.}
{I/O}
{User queries a string that doesn't match artists on any streaming services.}

\noindent{\textbf{Functional Req 9.}

\req{Valid Album Search Results}
{When a user chooses to query an album, and results for that album indeed exist, then they will be taken to a new page and presented with a list of albums of that name.}
{To give the user a list of common albums matching the desired name.}
{I/O}
{User queries an album that is present on streaming services}

\noindent{\textbf{Functional Req 10.}

\req{Invalid Album Search Results}
{When a user chooses to query an album, and no results for that name are found, then they will be taken to a new page and presented with "no albums found". }
{To inform the user that their query did not return any results.}
{I/O}
{User queries a string that doesn't match albums on any streaming services.}

\noindent{\textbf{Functional Req 11.}

\req{Unique Link Generation}
{When a user has a list of results from a valid query, they are able to click "generate link" for the desired result, which they can then copy and share with anyone}
{A unique link for a song, artist, or album is a more compact, easier way to share music with a friend.}
{I/O}
{User queries a valid song, artist, or album and is on the results page.}

\noindent{\textbf{Functional Req 12.}

\req{Create User}
{On the homepage, there are fields and a submission button for creating an account}
{User can have an account registered with the service, which will automatically keep track of all links and the date in which they are generated}
{I/O}
{User is on homepage}

\noindent{\textbf{Functional Req 13.}

\req{User Login}
{On the homepage, there are fields and a submission button for logging in as user}
{User can have an account registered with the service, which will automatically keep track of all links and the date in which they are generated}
{I/O}
{User is on homepage}


\newpage
\section*{Non-Functional Requirements}

\noindent{\textbf{Non-Funcitonal Req 1.}

\req{Query timeout after 10 seconds}
{When a user types an input, the website will take 10 seconds to filter results before timing out}
{Prevent vague queries from making expensive calls to APIs or database}
{I/O}
{User types input}

\noindent{\textbf{Non-Funcitonal Req 2.}

\req{Navigating the website from start to finish should take 3 clicks at most}
{The first click should choose the search result type, the second should highlight the search bar, and the third should click the desired result}
{A maximum of 3 clicks to get to the desired result keeps the website simple and user friendly}
{I/O}
{User experience navigating website}

\noindent{\textbf{Non-Funcitonal Req 3.}

\req{Optimize User Interface for all browser types and screen sizes}
{The website should maintain its intended look regardless of screen size or browser type}
{This prevents users from experiencing glitchy software}
{I/O}
{Browser types & Devices}

\noindent{\textbf{Non-Funcitonal Req 4.}

\req{Utilize MVC design pattern}
{Develop with model, view, controller design pattern using Flask framework}
{Website routing will be kept simple and minimal with MVC}
{I/O}
{Development}

\noindent{\textbf{Non-Funcitonal Req 5.}

\req{Use continuous integration}
{Configure a continuous integration client to keep current build updated}
{Keep each check-in verified by an automated build, allowing us to detect problems early}
{I/O}
{Version Control}

\noindent{\textbf{Non-Funcitonal Req 6.}

\req{Extensive testing}
{All code written should have extensive coverage}
{More code coverage in testing leads to less bugs in production code}
{I/O}
{Testing}

\noindent{\textbf{Non-Funcitonal Req 7.}

\req{Reusability}
{Write code that can be used for multiple tasks}
{Keep application lightweight and cut down on unnecessary code}
{I/O}
{Development}

\noindent{\textbf{Non-Funcitonal Req 8.}

\req{Scalability}
{Keep all practices within application suitable for large and small amounts of data}
{Develop with scalability as a priority to keep application fast regardless of traffic and use}
{I/O}
{Development}

\noindent{\textbf{Non-Funcitonal Req 9.}

\req{Security}
{Deploy application with virtual environment so no keys are kept in plain text}
{No keys kept in plain text to maximize security and minimize vulnerability}
{I/O}
{Deployment}

\noindent{\textbf{Non-Funcitonal Req 10.}

\req{Reliability}
{Application should respond the same regardless of website traffic }
{Keep users satisfied and maintain ease of use}
{I/O}
{Development/Deployment}
